\documentclass{article}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{caption}
\usepackage[utf8]{inputenc}
  \usepackage[
    backend=biber,
    style=ieee,
  ]{biblatex}
 


\title{CS6000 - Tenth Assignment}
\author{Marc Moreno Lopez}
\date{November 26th 2018}

\begin{document}

\maketitle

\section{Report}

%In your final journal, I'd like you to reflect back over the course and what you think was the most significant learning experiences and why.  Then reflect on what was the least and why. 

This course has helped me understand many thing way better and has also introduced new concepts. At the beginning, when I started the class, I didn't know what to expect. I was afraid it was going to be one of those mandatory classes that you have to take but you learn nothing from it. But it was completely wrong. This has been a great class and the most useful class that I have taken from my Masters and my PhD. 

One of the things that I valued the most from this class was getting insight from Dr. Boult in so many aspects like reviewing, publishing and writing a paper. It is something incredibly valuable and I have learned a lot in just a semester. Learning and listening to his experiences is something great and it changed my perspective on the publishing and conferences world. One class that I really liked and that I thought that it was really helpful was the class on the timeline for the PhD. Before enrolling into the PhD program I already knew about the exams and proposals, but I wish I would have known more about it before starting. I think that this class could be done at the beginning of each semester for new PhD students. That way the students would have a more defined timeline when they start their PhD. 

As I stated in the Journal 9, learning how to use AWS was something great. The cloud computing assignment helped me see how easy it is to use cloud computing and all the benefits that it has. I would have loved to do something a bit more related to deep learning, with GPUs involved. This is something that I'll definitely do in the future and that I'm looking forward to learning more. The survey paper was also a great experience and a major learning point from this class. I had done another survey paper before this class, but doing it in a field related to my research was more enjoyable and made it a better experience overall. During some weeks, I struggled due to my workload and because I was missing some key elements. Finding a good story was probably the most difficult part, together with finding the major categories for the paper. The class where we talked about statistics and their importance was a bit confusing for me. I understand why they are important and why we should use them. However, metrics in every research area are different and sometimes statistics aren't as useful and detailed as the metrics that people use in that area (precision, recall, DICE score ...).

As a side note, I wish we had had more talks from university faculty. I have been at UCCS for 3.5 years and I would like to know more about the research that is done and what other teachers are working on. I think this class is a chance for them to talk about their research and connect with new students. This could be a really good way to forge new partnerships between students and faculty members. 

Overall, this class has been a great learning experience and one of my favorite classes at UCCS. I feel like I have learned a lot and I feel more prepared to work on my research and publish in conferences/journals. I wish I would have taken it earlier! 

Inside my repo I have cloned the overleaf project. In this folder you can find all the files for the tex file.


\end{document}
